Timeliness of security updates for Android

### 2014-08-06 securityupdates.tex
Expand intro to Background

\section{Background}
\label{sec:background}
There are two sources of data we needed for this study, information on root exploits and information on installed versions of Android.

>>>>

\section{Background}
\label{sec:background}
There are two sources of data we needed for this study, information on root vulnerabilities and information on installed versions of Android.
We need data on root vulnerabilities so that we know which versions of Android were vulnerable to which known vulnerabilities at what times.
We need information on the distribution of installed versions of Android so that we know what proportion of Android devices were affected by these vulnerabilities.
